Rutgers Autonomous Aircraft Team\\Technical Report\\2010 AUVSI UAS Competition

### 2010-05-24 paper/paper.tex
spel chek

For this entry, we took a close look at our goals and requirments, and dialed back our approach to ensure we would meet the most basic competition requirments successfully.
We started the design with some broad goals based on our experience in the 2009 competition. 
Sub-teams and individuals tackled the smaller problems while still keeping an eye on the big picture.

@@

We elected to persue a kit-type airplane rather than our own design. 
Our own custom design, the \emph{Icarus}, suffered a catastrophic structural failure last year. From this, we learned that custom structures require much more testing and revision than a proven kit. We also reconsidered our payload requirments and decided we could easily modify a kit plane to accept our autopilot and imaging system.

@@

A member of our local R/C club, Tri-County RC \cite{tricountyRC}, donated a ten-foot wingspan high wing trainer to our club. The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flightworthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered, we tested the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 3.5 lbs electronics payload, would bring the maximum takeoff weight to 25.5lbs.

We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test similar to mimic the 
Federal Airworthiness Standards' structural requirments\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. accelleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ accelleration, with a saftey factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

The plane was carefully supported under the center section, nose, and tail while pre-weighed bags of sand were slowly placed symetrically and simultaneously on the underside of each wing, starting from the innermost rib.  The \emph{Daedalus} wings supported 64 lbs (250\% of the maximum take-off weight) under static loading.  We also rocked the plane ten degrees from side to side while fully loaded to simulate differential loads during flight. Our post-test structure inspection found no warped members or cracked joints.

A second test was designed to certify the wing could take a top loading present from a 1.5$g$ accelleration with a saftey factor of 1.5, and to certify that load could be transmitted to the ground through the fuselage and landing gear. With the aircraft fully assembled and sitting upright on the landing gear, we loaded the top of the wing along the quarter chord with 64 lbs of sandbags. As in our first test, we also rocked the plane \degrees{10} side to side to simulate uneven loading. Our post-test structure inspection found no warped members or cracked joints.

Satisfied, made engine and surface tests (see \ref{sec:appendix_preflight}) before taxiing the plane around a parking lot.  We brought the plane back inside, examined it for signs of stress and, finding everything in good condition, deemed the \emph{Daedalus} flightworthy.

@@

Each airframe has a 45cc gasoline engine and 24 ounce gasoline tank. Based on our flight tests, with climbs to 400 feet AGL and a high throttle cruise, we use a little less than 1oz gasoline per minute. While actual fuel consumption may be less, we set a flight time cap at 20 minutes in order to always have a saftey reserve of at least 4oz. We have tested to ensure that, within \degrees{\pm10} of level flight, the fuel tank will feed the engine until less than $1/2$oz fuel remains.

@@

\subsection{Requirments}

@@

We took advantage of the MHS-PM5's swiveling lens assembley 
(see Figure \ref{fig:camera_frontview}, and added a servo actuator which could rotate the lens \degrees{135} back from straight forward, as shown in Figure \ref{fig:pantilt_linkdetail}. The tilt servo is a Hitech HS 77BB \ref{hitechs77bb}, and is capable of \degrees{180} rotation.
The camera and tilt servo assembley is attached to the aircraft on a rotating mount. A thrust bearing takes lateral loads off the pan servo shaft, and stabilizes the assembley. The pan servo is a Hitech HS 785HB \ref{hitechhs785}, and is capable of \degrees{720} rotation. Both servos are powered and controlled by the Camera Control board.

The total height of the imaging system is 8.75", only 4'' of which is exposed below the fuselage of the aircraft. The rotating assembly is, on its widest dimension 2.13", and would fit inside a 2.5" cylinder. Wires exiting the side of the camera, inside the fuselage, may make the assebley a bit wider. Because the maximum rotation is only \degrees{270}, the camera and tilt servo wires only have to be capable of wrapping \degrees{\pm 360} around the shaft below the thrust bearing. A wire guide will be added to keep the wires from tangling once construction of the pan-tilt is complete.

@@

We consider the safety of our team, our aircraft, and our spectators to be of utmost importance.  As such, we've implemented numerous safety features and developed a strict procedure for starting, taxiing, and flying the plane.  This procedure enables us to ensure that all personnel are safely in place, and that no intergral checks are missed.

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby. 
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction.
	\item If the plane loses contact with the ground station for more than XX seconds, the autopilot will default to a ``return home mode'' that will direct the plane towards the groundstation in hopes of reestablishing a connection.  If the connection remains dead for XX minutes, the autopilot will direct the plane to [DO SOMETHING?]
	\item Channel 6 (?) functions as a remote kill switch, ensuring the ability to cut power to the engine if an emergent situation precludes direct manual shut off.
	\item etc?
\end{itemize}

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Pre-flight Procedures}
\label{sec:appendix_preflight}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extentions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen\footnotemark, centerman\footnotemark.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``reciever on''.  Centerman turns on reciever, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Starter primes engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledges.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.

>>>>

For this entry, we took a close look at our goals and requirements, and dialed back our approach to ensure we would meet the most basic competition requirements successfully.
We started the design with some broad goals based on our experience in the 2009 competition. 
Sub-teams and individuals tackled the smaller problems while still keeping an eye on the big picture.

@@

We elected to pursue a kit-type airplane rather than our own design. 
Our own custom design, the \emph{Icarus}, suffered a catastrophic structural failure last year. From this, we learned that custom structures require much more testing and revision than a proven kit. We also reconsidered our payload requirements and decided we could easily modify a kit plane to accept our autopilot and imaging system.

@@

A member of our local R/C club, Tri-County RC \cite{tricountyRC}, donated a ten-foot wingspan high wing trainer to our club. The plane, first built out of foam and balsa from long-lost plans in 1986, was accepted graciously, but required quite a bit of work before it was once again flight-worthy. We removed the covering to find water damage and rot which resulted from years of storage. We stripped and rebuilt nearly the entire airframe, adding carbon-fiber reinforcements to the wing in anticipation of increased wing loading due to our payload. Once rebuilt and covered, we tested the \emph{Daedalus} weighed 19.5 lbs with engine. A full 24oz fuel tank, plus 3.5 lbs electronics payload, would bring the maximum takeoff weight to 25.5lbs.

We wanted to certify the wings and wing root would withstand large dynamic forces in flight. 
We designed a test similar to mimic the 
Federal Airworthiness Standards' structural requirements\footnote{Special Federal Aviation Regulation No. 23, Subpart C--Structure. Assuming full load on wing as described in 23.335 paragraph 4.i., where an aircraft must pull out of a \degrees{7.5} dive at cruise velocity and cruise power ``with a load factor of 1.5 (0.5$g$. acceleration increment)'' \cite{far23}}. Our first test was designed to certify that the wing, supported at the wing root and fuselage, could take a bottom loading present in a 1.5$g$ acceleration, with a safety factor of 1.5\footnote{As stated in 23.303 \cite{far23}.}.

The plane was carefully supported under the center section, nose, and tail while pre-weighed bags of sand were slowly placed symmetrically and simultaneously on the underside of each wing, starting from the innermost rib.  The \emph{Daedalus} wings supported 64 lbs (250\% of the maximum take-off weight) under static loading.  We also rocked the plane ten degrees from side to side while fully loaded to simulate differential loads during flight. Our post-test structure inspection found no warped members or cracked joints.

A second test was designed to certify the wing could take a top loading present from a 1.5$g$ acceleration with a safety factor of 1.5, and to certify that load could be transmitted to the ground through the fuselage and landing gear. With the aircraft fully assembled and sitting upright on the landing gear, we loaded the top of the wing along the quarter chord with 64 lbs of sandbags. As in our first test, we also rocked the plane \degrees{10} side to side to simulate uneven loading. Our post-test structure inspection once again found no warped members or cracked joints.

Satisfied, made engine and surface tests (see \ref{sec:appendix_preflight}) before taxiing the plane around a parking lot.  We brought the plane back inside, examined it for signs of stress and, finding everything in good condition, deemed the \emph{Daedalus} flight-worthy.

@@

Each airframe has a 45cc gasoline engine and 24 ounce gasoline tank. Based on our flight tests, with climbs to 400 feet AGL and a high throttle cruise, we use a little less than 1oz gasoline per minute. While actual fuel consumption may be less, we set a flight time cap at 20 minutes in order to always have a safety reserve of at least 4oz. We have tested to ensure that, within \degrees{\pm10} of level flight, the fuel tank will feed the engine until less than $1/2$oz fuel remains.

@@

\subsection{Requirements}

@@

We took advantage of the MHS-PM5's swiveling lens assembly 
(see Figure \ref{fig:camera_frontview}, and added a servo actuator which could rotate the lens \degrees{135} back from straight forward, as shown in Figure \ref{fig:pantilt_linkdetail}. The tilt servo is a Hitech HS 77BB \ref{hitechs77bb}, and is capable of \degrees{180} rotation.
The camera and tilt servo assembley is attached to the aircraft on a rotating mount. A thrust bearing takes lateral loads off the pan servo shaft, and stabilizes the assembly. The pan servo is a Hitech HS 785HB \ref{hitechhs785}, and is capable of \degrees{720} rotation. Both servos are powered and controlled by the Camera Control board.

The total height of the imaging system is 8.75", only 4'' of which is exposed below the fuselage of the aircraft. The rotating assembly is, on its widest dimension 2.13", and would fit inside a 2.5" cylinder. Wires exiting the side of the camera, inside the fuselage, may make the assembly a bit wider. Because the maximum rotation is only \degrees{270}, the camera and tilt servo wires only have to be capable of wrapping \degrees{\pm 360} around the shaft below the thrust bearing. A wire guide will be added to keep the wires from tangling once construction of the pan-tilt is complete.

@@

We consider the safety of our team, our aircraft, and our spectators to be of utmost importance.  As such, we've implemented numerous safety features and developed a strict procedure for starting, taxiing, and flying the plane.  This procedure enables us to ensure that all personnel are safely in place, and that no integral checks are missed.

\subsection{Safety Features}
Our system is designed to gracefully handle any failure while continuing to ensure the safety of those nearby. 
\begin{itemize}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Channel 5 (?) allows quick switch to safety pilot in case of autopilot malfunction.
	\item If the plane loses contact with the ground station for more than XX seconds, the autopilot will default to a ``return home mode'' that will direct the plane towards the ground station in hopes of reestablishing a connection.  If the connection remains dead for XX minutes, the autopilot will direct the plane to [DO SOMETHING?]
	\item Channel 6 (?) functions as a remote kill switch, ensuring the ability to cut power to the engine if an emergent situation precludes direct manual shut off.
	\item etc?
\end{itemize}

@@

\newpage
\appendix
\renewcommand\thesection{Appendix \Alph{section}}
\section{Pre-flight Procedures}
\label{sec:appendix_preflight}
\begin{enumerate}
	\setlength{\itemsep}{0cm}
	\setlength{\parskip}{0cm}
	\item Assemble plane.
	\item Check all mechanical and electrical connections.
		\begin{itemize}
		\itemspace
		\item Are all nuts/bolts loc-tited?
		\item Are all servo extensions connected and properly secured?
		\item Are all access hatches secured?
		\end{itemize}
	\item Position wingmen\footnotemark, centerman\footnotemark.
	\item Pilot turns on transmitter, announces ``transmitter on.''
	\item Pilot requests ``receiver on''.  Centerman turns on receiver, acknowledges.
	\item Pilot completes surface checks:
		\begin{itemize}
		\itemspace
		\item Ailerons
		\item Elevator
		\item Rudder
		\item Throttle
		\end{itemize}
	\item Starter primes engine.
	\item Pilot obtains visual and verbal confirmation that wingmen, centerman are in place and alert.
	\item Pilot requests ``ignition on.''  Centerman moves ignition switch to the ``on'' position and acknowledges.
	\item Starter requests ``prop clear.''  Starter obtains visual confirmation that no person is standing in the prop arc and announces ``prop clear.''
	\item Starter announces ``contact'' and starts the engine.
	\item Starter clears the area.
	\item Pilot repeats surface and throttle checks at close range.
	\item Pilot leaves starting area and performs surface and throttle checks from a distance (range test).
	\item Pilot returns to starting area to prepare for taxi.
	\item Pilot requests ``centerman off.''  Centerman carefully clears the area and acknowledges.
	\item Pilot requests ``wingmen off.''  Wingmen carefully clear the area and acknowledge.
	\item Pilot taxis airplane to appropriate location to begin takeoff.
	\item Pilot commences takeoff.
